---
title: "Enrichment"
author:
- name: Y-h. Taguchi
  affiliation:  Department of Physics, Chuo University, Tokyo 112-8551, Japan
  email: tag@granular.com
output:   
    BiocStyle::html_document:
    toc: true
bibliography: references.bib
vignette: >
  %\VignetteIndexEntry{Enrichment}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r style, echo = FALSE, results = 'asis'}
BiocStyle::markdown()
```

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  crop = NULL,
  comment = "#>"
)
```



```{r setup}
library(TDbasedUFE)
library(TDbasedUFEadv)
```

# Introduction

It might be helpful to demonstrate how to evaluate selected genes by enrichment analysis. Here, we show some of useful tools applied to the output from TDbasedUFEadv
For this purpose, we use a bundled subset of TCGA RNA-seq data originally distributed in RTCGA.rnaseq, together with clinical conditions derived from RTCGA.clinical. The subset contains 100 samples and 1,000 genes for each of BLCA, BRCA, CESC, and COAD. The original package versions and subset indices are recorded in the source element of the bundled data.

``` {r}
example <- readRDS(system.file(
  "extdata", "enrichment_example.rds",
  package = "TDbasedUFEadv",
  mustWork = TRUE
))

Multi <- example$Multi
Z <- prepareTensorfromList(Multi, 10L)
Z <- aperm(Z, c(2, 1, 3))
Z <- PrepareSummarizedExperimentTensor(
  feature = example$feature,
  sample = array("", 1), value = Z,
  sampleData = example$cond
)
HOSVD <- computeHosvd(Z)
cond <- attr(Z, "sampleData")
index <- selectFeatureProj(HOSVD, Multi, cond, de = 1e-3, input_all = 3) # Batch mode
head(tableFeatures(Z, index))
genes <- unlist(lapply(strsplit(tableFeatures(Z, index)[, 1], "|",
  fixed = TRUE
), "[", 1))
entrez <- unlist(lapply(strsplit(tableFeatures(Z, index)[, 1], "|",
  fixed = TRUE
), "[", 2))
```

# Enrichr 

Enrichr[@Enrichr] is one of tools that often provides us significant results 
toward genes selected by TDbasedUFE and TDbasedUFEadv.

```{r enrichr-example, eval=FALSE}
if (!requireNamespace("enrichR", quietly = TRUE)) {
    stop("The enrichR package is required to run this example.")
}

enrichR::setEnrichrSite("Enrichr")

dbs <- c(
    "GO_Molecular_Function_2015",
    "GO_Cellular_Component_2015",
    "GO_Biological_Process_2015"
)

enriched <- enrichR::enrichr(genes, dbs)

enrichR::plotEnrich(
    enriched$GO_Biological_Process_2015,
    showTerms = 20,
    numChar = 40,
    y = "Count",
    orderBy = "P.value"
)
```

Enrichr can provide you huge number of enrichment analyses, 
many of which have good compatibility with the genes selected by
TDbasedUFE as well as TDbasedUFEadv by the experience. 
Please check Enrichr's web site to see what kinds of enrichment
analyses can be done.

# STRING

STRING[@STRING] is enrichment analyses based upon protein-protein interaction, 
which is known to provide often significant results toward genes selected by
TDbasedUFE as well as TDbasedUFEadv.

```{r stringdb-example, eval=FALSE}
if (!requireNamespace("STRINGdb", quietly = TRUE)) {
    stop("The STRINGdb package is required to run this example.")
}

string_cache <- tools::R_user_dir("TDbasedUFEadv", which = "cache")
dir.create(string_cache, recursive = TRUE, showWarnings = FALSE)

string_db <- STRINGdb::STRINGdb$new(
    version = "11.5",
    species = 9606,
    score_threshold = 200,
    network_type = "full",
    input_directory = string_cache
)

example1_mapped <- string_db$map(
    data.frame(genes = genes),
    "genes",
    removeUnmappedRows = TRUE
)

hits <- example1_mapped$STRING_id
string_db$plot_network(hits)
```

# enrichplot

Although these above can provide us enough number of information to evaluate 
the genes selected by TDbasedUFE as well as TDbasedUFEadv, one might need 
all one package for which one does not how to decide which category must
be evaluated in enrichment analysis.

In this case, we would recommend Metascape[@Metascape] that unfortunately  
does not have the ways approached from R. Thus, we recommend RITAN as
an alternative. It can list significant ones among multiple categories.


```{r dose-example}
if (
    requireNamespace("DOSE", quietly = TRUE) &&
    requireNamespace("enrichplot", quietly = TRUE) &&
    requireNamespace("gson", quietly = TRUE) &&
    requireNamespace("ggplot2", quietly = TRUE)
) {
    edo <- DOSE::enrichDGN(entrez)

    enrichplot::dotplot(edo, showCategory = 30) +
        ggplot2::ggtitle("dotplot for ORA")
} else {
    message(
        "Skipping DOSE/enrichplot example because one or more optional packages ",
        "are not installed: DOSE, enrichplot, gson, ggplot2."
    )
}
```
```{r}
sessionInfo()
```

