---
title: "TDbasedUFEadv"
author:
- name: Y-h. Taguchi
  affiliation:  Department of Physics, Chuo University, Tokyo 112-8551, Japan
  email: tag@granular.com
output:   
    BiocStyle::html_document:
    toc: true
vignette: >
  %\VignetteIndexEntry{TDbasedUFEadv}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r style, echo = FALSE, results = 'asis'}
BiocStyle::markdown()
```

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
#library(TDbasedUFEadv)
```

# Introduction 

Since TDbasedUFEadv is an extended package from TDbasedUFE, please master the 
contents in TDbasedUFE prior to the trial of this package. 

# Integrated analysis of two omics data sets


## When features are shared.

### Full tensor 

Suppose we have two omics profiles
$$
x_{ij} \in \mathbb{R}^{N \times M} \\
x_{ik} \in \mathbb{R}^{N \times K}
$$
that repesent values of $i$th feature  of $j$th and $k$th objects, respectively 
(i.r., these two profiles share the features).
In this case, we generate a tensor, $x_{ijk}$, by the product of two profiles as
$$
x_{ijk} =  x_{ij}x_{ik} \in \mathbb{R}^{N \times M \times K}
$$

and HOSVD was applied to $x_{ijk}$ to get
$$
x_{ijk} = \sum_{\ell_1} \sum_{\ell_2} \sum_{ell_3} G(\ell_1 \ell_2 \ell_3) 
u_{\ell_1 i} u_{\ell_2 j} u_{\ell_3 k}
$$
After that we can follow the standard procedure to select features $i$s
associated with the desired properties represented by the selected signular
value vectors, $u_{\ell_2 j}$ and $u_{\ell_3 k}$, arrtibuted to objects,
$j$s and $k$s.

### Matrix generated by patial summation 

In the above, we dealt with full tensor. It is often difficult to treat full 
tensor, since it is as large as $N \times M times K$. In this case, we can take
the alternative approach. In order that we define reduced matix with taking 
partial summation
$$
x_{jk} = \sum_i x_{ijk}
$$
and apply SVD to $x_{jk}$ as
$$
x_{jk} = \sum_\ell \lambda_\ell u_{\ell j} v_{\ell k}
$$
and sigular value vectors attributed to samples as
$$
u^{(j)}_{\ell i} = \sum_j u_{\ell j} x_{ij} \\
u^{(k)}_{\ell k} = \sum_k v_{\ell k} x_{ik}
$$
In this case, signular value vectors are attributed separately to features
associated with objects $j$ and $k$, respectively.

The feature selection can be done using these singular value vectors associated
with selected sigular value vectors attributed to samples, $j$ and $k$.

## When samples are shared.

### Full tensor
In the case where not features but samples are shared between two omics data, 
we can do something similar.
$$
x_{ij} \in \mathbb{R}^{N \times M} \\
x_{kj} \in \mathbb{R}^{K \times M}
$$


In this case, we generate a tensor, $x_{ijk}$, by the product of two profiles as
$$
x_{ijk} =  x_{ij}x_{kj} \in \mathbb{R}^{N \times M \times K}
$$

and HOSVD was applied to $x_{ijk}$ to get
$$
x_{ijk} = \sum_{\ell_1} \sum_{\ell_2} \sum_{ell_3} G(\ell_1 \ell_2 \ell_3) 
u_{\ell_1 i} u_{\ell_2 j} u_{\ell_3 k}
$$
After that we can follow the standard procedure to select features $i$s and $k$s
associated with the desired properties represented by the selected singular
value vectors, $u_{\ell_2 j}$, arrtibuted to objects, $j$s.

###  Matrix generated from partila summation

In the above, we dealt with full tensor. It is often difficult to treat full 
tensor, since it is as large as $N \times M times K$. In this case, we can take
the alternative approach. In order that we define reduced matix with taking 
partial summation
$$
x_{ik} = \sum_j x_{ijk}
$$
and apply SVD to $x_{jk}$ as
$$
x_{ik} = \sum_\ell \lambda_\ell u_{\ell i} v_{\ell k}
$$
and sigular value vectors attributed to features as
$$
u_{\ell i} = \sum_j u_{\ell i} x_{ij} \\
u_{\ell k} = \sum_j v_{\ell k} x_{kj}
$$



```{r}
sessionInfo()
```
