---
title: "TDbasedUFEadv"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{TDbasedUFEadv}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
#library(TDbasedUFEadv)
```

# Introduction 

Since TDbasedUFEadv is an extended package from TDbasedUFE, please master the contents in TDbasedUFE prior to the trial of this package. 

# Integrated analysis of two omics data sets

Suppose we have two omics profiles
$$
x_{ij} \in \mathbb{R}^{N \times M} \\
x_{ik} \in \mathbb{R}^{N \times K}
$$
that repesent values of $i$th feature  of $j$th and $k$th objects, respectively (i.r., these two profiles share the features).
In this case, we generate a tensor, $x_{ijk}$, by the product of two profiles as
$$
x_{ijk} =  x_{ij}x_{ik} \in \mathbb{R}^{N \times M \times K}
$$

and HOSVD was applied to $x_{ijk}$ to get
$$
x_{ijk} = \sum_{\ell_1} \sum_{\ell_2} \sum_{ell_3} G(\ell_1 \ell_2 \ell_3) u_{\ell_1 i} u_{\ell_2 j} u_{\ell_3 k}
$$
After that we can follow the standard procedure to select features $i$s associated with the desirred properties reprented by the selected signular value vectors, $u_{\ell_2 j}$ and $u_{\ell_3 k}$, arrtibuted to ojjects, $j$s and $k$s.

